Calculating life expectancy and exploring missingness

### 2016-10-27 Code/1_Explore_Data_v2.Rmd

```{r}
first <- list.cod.decomp.tables[[1]]
first$sign <- ifelse(first$C_xi < 0, "negative", "positive")
first$group <- interaction(first$Ages, first$sign, sep = ".")

first <- first %>% 
  arrange(Ages, sign, Cause.of.death) %>%
  group_by(group) %>%
  mutate(lag = lag(C_xi), one = 1, 
         num = cumsum(one),
         length = n(),
         start = ifelse(is.na(lag)==T, 0, NA),
         finish = ifelse(is.na(lag)==T, C_xi, NA))
View(first)

updated <- NULL
for (g in unique(first$group)) {
  subset <- first[first$group == g, ]

  if(dim(subset)[1] > 1){
      for (i in 2:dim(subset)[1]) {
        subset$start[i] <- subset$finish[i - 1]
        subset$finish[i] <- subset$start[i] + subset$C_xi[i]
      }
  }

  updated <- rbind(updated, subset)
}
updated 
```

@@

```{r}
save(dat.clean, dat2, BlackWhite, paired.ids, list.age.decomp.tables,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```

>>>>

```{r  update_decomp_for_plotting}
#update the decomposition table for plotting purposes
for(i in 1:dim(paired.ids)[1]) {
    if(list.cod.decomp.tables[[i]][1] != "Couldn't compare life tables") { 
        list.cod.decomp.tables[[i]] <- 
                              make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables[[i]], 
                              age.groups = "Ages", 
                              cause.of.death = "Cause.of.death")  
    } 
  print(i)
}  
```

```{r pretty_cod}
ggplotly(ggplot(list.cod.decomp.tables[[1]], aes(y = Ages, x = start)) + 
           geom_segment(aes(xend = finish, col = Cause.of.death, yend = Ages), lwd = 4) +
           xlab("Contribution to life expectancy gap") +
           ylab("Age group\n") + theme_minimal() +
           geom_vline(xintercept = 0))
```

@@

```{r}
save(dat.clean, dat2, BlackWhite, paired.ids, list.age.decomp.tables, list.cod.decomp.tables,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```
